Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2016-10-02 paper.tex
Clarify which drag coefficient in figure br-cfd-perf-bar-chart
Explain why we care about TKE

    \caption{Power (left) and drag (right) coefficient predictions at $\lambda =
    1.9$, from experiments and each numerical model.}

@@

Turbulence kinetic energy profiles are also shown in
Figure~\ref{fig:br-cfd-profiles}. The turbulence kinetic energy for the unsteady
RANS models was calculated as
\begin{equation}
    k = k_{\mathrm{RA}} + \frac{1}{2} \left(
    \overline{U^\prime}^2 +
    \overline{V^\prime}^2 +
    \overline{W^\prime}^2 \right),
    \label{eq:k}
\end{equation}
where $U^\prime = U - \overline{U}$ (the resolved velocity fluctuations) and
$k_{\mathrm{RA}}$ is the kinetic energy calculated by the turbulence model,
which is zero for the SA model.

>>>>

    \caption{Power (left) and rotor drag (right) coefficient predictions at
    $\lambda = 1.9$, from experiments and each numerical model.}

@@

Since this is a relatively high Reynolds number flow, it was of interest to
evaluate turbulence predictions, since these will play an important role in
overall flow dynamics. Validation was performed against the UNH-RVAT's
experimental dataset, which was acquired via acoustic Doppler velocimetry. The
turbulence kinetic energy for the unsteady RANS models was calculated as
\begin{equation}
    k = k_{\mathrm{RA}} + \frac{1}{2} \left(
    \overline{U^\prime}^2 +
    \overline{V^\prime}^2 +
    \overline{W^\prime}^2 \right),
    \label{eq:k}
\end{equation}
where $U^\prime = U - \overline{U}$ (the resolved velocity fluctuations) and
$k_{\mathrm{RA}}$ is the kinetic energy calculated by the turbulence model,
which is zero for the SA model. Profiles from the simulation results are shown
in Figure~\ref{fig:br-cfd-profiles}.
